Interpretable Machine Learning

### 2018-03-27 talk.Rmd
pdates slides with iml package

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.randomForest', importance=TRUE)
mod = train(lrn, task)
```
## Step 3: Profit. {.center}

@@

```{r}
ice = generatePartialDependenceData(mod, task, features ='Age', 
                                    individual = TRUE)
plotPartialDependence(ice) + scale_y_continuous(limits=c(0, NA))
```

@@

```{r}
ice.c = generatePartialDependenceData(mod, task, features ='Age', 
          individual = TRUE, center = list(Age=20))
plotPartialDependence(ice.c)
```

@@

```{r}
pdp = generatePartialDependenceData(mod, task, features =c('Age'))
plotPartialDependence(pdp) + scale_y_continuous(limits=c(0, NA))
```

@@

```{r, warning=FALSE}
feat.imp = getFeatureImportance(mod, type=1)$res
dat = gather(feat.imp, key='Feature', value='Importance') %>% arrange(Importance)
dat$Feature = factor(dat$Feature, levels = dat$Feature)
ggplot(dat)  + geom_point(aes(y=Feature, x = Importance))
```

@@

```{r}
pdp = generatePartialDependenceData(mod, task, features =c('Gender'))
ggplot(pdp$data) + geom_point(aes(x=Gender, y=CompensationAmount)) + 
  geom_segment(aes(x=Gender, xend=Gender, yend=CompensationAmount), y=0) + 
  scale_y_continuous(limits=c(0, NA)) + 
  theme(axis.text.x = element_text(angle = 10, hjust = 1))
```

@@

## 
```{r, echo=FALSE, fig.align='center'}
set.seed(44)
dat = getTaskData(task)
```
```{r, echo=TRUE, fig.align='center'}
explanation <- lime(dat, mod)
explainer <- lime::explain(dat[3, ], explanation, n_features = 3)
plot_features(explainer, ncol=1)
```

@@

>>>>

## Step 2: Throw ML on your data
```{r learn, warning=FALSE}
library('mlr')
set.seed(42)
task = makeRegrTask(data = survey.dat, target = 'CompensationAmount')
lrn = makeLearner('regr.gbm', interaction.depth = 4, n.trees = 500)
mod = train(lrn, task)
```
## Step 3: Profit. {.center}

@@

```{r}
library("iml")
X = survey.dat[-which(names(survey.dat) == "CompensationAmount")]
predictor = Predictor$new(mod, data = X, y = getTaskTargets(task))
ice = Ice$new(predictor, feature ='Age')
ice$plot()
```

@@

```{r}
ice$center(20)$plot()
```

@@

```{r}
pdp = PartialDependence$new(predictor, feature = "Age")
pdp$plot()
```

@@

```{r, warning=FALSE}
feat.imp = FeatureImp$new(predictor, loss = 'mae')
feat.imp$plot()
```

@@

```{r}
pdp = PartialDependence$new(predictor, feature="Gender")
pdp$plot() 
```

@@

## 
```{r, echo=FALSE, fig.align='center'}
set.seed(44)
```

```{r, echo=TRUE, fig.align='center', message = FALSE}
explanation = LocalModel$new(predictor)
explanation$explain(X[5, ])$plot()
```

@@

# Shapley

## 
```{r, echo=FALSE, fig.align='center'}
set.seed(44)
```

```{r, echo=TRUE, fig.align='center'}
explanation = Shapley$new(predictor)
explanation$explain(X[5, ])$plot()
```
